Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants with Transient Performance Specifications

### 2017-05-25 automatica/automatica.tex
assigned sections to collaborators
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{abstract}                          % Abstract of not more than 200 words.
\textcolor{red}{We have to write a new abstract.}
\end{abstract}

@@

\section{Introduction}
\textcolor{red}{We have to write a new introduction as well.}

@@

@@

\textcolor{red}{this section needs to be updated to describe about floating-point arithmetic.}

@@

{\color{red} It must be carefully described: it will be an important contribution}

@@

@@

@@

@@

@@

\textcolor{red}{We need to write a new conclusions about this work.}

>>>>

\begin{abstract}                          % Abstract of not more than 200 words.
\textcolor{red}{Lucas: We have to write a new abstract.}
\end{abstract}

@@

\section{Introduction}
\textcolor{red}{Cristina: We have to write a new introduction as well.}

@@

\textcolor{red}{Elizabeth: we need to define the notation used throughout the paper.}

@@

\textcolor{red}{Elizabeth: this section needs to be updated to describe about floating-point arithmetic.}

@@

{\color{red} Dario: this section must be carefully described: it will be an important contribution}

@@

\textcolor{red}{Iury: can you please describe the benchmarks?}

@@

\textcolor{red}{Lucas: describe here the experimental objectives.}

@@

\textcolor{red}{Pascal: can you please describe here the experimental results?}

@@

\textcolor{red}{Pascal: can you please describe here the threats to validity?}

@@

\textcolor{red}{Lucas: We need to write a new conclusions about this work.}
